Towards the Internet of Things: A Real-World Testbed

### 2013-06-14 trunk/doc/paper- towards the internet of things/paper v1.tex

\subsection{Mobile client}
The mobile client application is an interactive application for android phones that enable users to get access to the real-time consumption of their homes and also to remotely control their appliance by turning on and off any appliance linked to some mote in the wireless sensor network. The mobile client when wanting to turn on or off some appliance sends a request directly towards the mote responsible for that action and designate the mote using its "vitual" IPV4 address that it does not own in really since it has an IPV6 address but that virtual IPV4 address is reserved for that mote and the translation is dealt with at the level of the gateway.

@@

@@

\subsection{Network gateway packet transformation}
This is a very important component in the system. The issue is the following. The WSN network supports only IPV6 while other components such as the middleware and the mobile client do not necessary have an IPV6 address, but we still want all the components to communicate independently of the IP technology to be used. To do so, we have created a network packet transformation program. This program basically converts IPV4 to IPV6 and vice versa. To do so, it assigns virtual IPV4 addresses to IPV6 address holders and and IPV6 address to IPV4 address holders. With such a program, each player in the network has both an IPV4 and an IPV6 but is aware of only the one that is assigned to him. The other "virtual" address is known only at the level of the program installed at the gateway station between the WSN and the outside world. The flow of information works as follow; when a station wants to send requests to a mote, it will send IPV4 packet holding the request to the mote but by addressing it using its virtual IPV4 address. This packet will be sniffed by this packet transformation program that will extract the TCP datagram from the ip packet, create a new IPV6 packet specifying the source address as the virtual address of the host and the destination as the address of the mote and then append the TCP datagram to the newly created packet and send it to the mote sink packet forwarding component that is seen by the gateway as a network interface card. This leads to a complicated issue that is to be handled and which is that the program should keep track of the request responses in order to forward them correctly to the destination. To solve such a problem, an algorithm has been created whose sole role is to mechanically compute the IPV6 address of the host based on its IPV4 and vice versa. This algorithm is based on function whose primary quality is the fact that it is bijective which means any IPV4 address is mapped to one and only one IPV6 function and vice versa. So whenever a request is coming, the source and destination address will be converted using this algorithm and this will make avoid the whole request response tracking part.
\section{Measurements}

@@

\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

>>>>

\subsection{Mobile client}
The mobile client application is an interactive application for android phones that enable users to get access to the real-time consumption of their homes and also to remotely control their appliance by turning on and off any appliance linked to some mote in the wireless sensor network. The mobile client when wanting to turn on or off some appliance sends a request directly towards the mote responsible for that action and designate the mote using its "virtual" IPV4 address that it does not own in really since it has an IPV6 address but that virtual IPV4 address is reserved for that mote and the translation is dealt with at the level of the gateway.

@@

\begin{figure}[htbp]
\centering
\includegraphics[height=110mm,width=90mm]{images/control_appliance_data_flow.jpg}
\caption{Data flow diagram for the mobile client sending on/off commands}
\label{fig:control_appliance}
\end{figure}

\
As one of the main goals of this project is to provide a two-way communication between the client and sensor, we will explain both way's flow of information. Figure 2 depicts the flow of information going from the client to the appliance. As the mobile client in the system is connected to a Wifi network that uses IPV4 and the mote is a network that uses a IPV6, then there should be a process that does some transformation to incoming and outgoing packets. So the client sends the packet to the virtual IPV4 address of the mote. The gateway receives it translates the virtual IPV4 address into the real IPV6 address of the mote and sets as source address the virtual IPV6 address of the mobile client. The new IPV6 packet is created holding the same payload as the original IPV4 packet. This new IPV6 packet is to be forwarded to the wireless sensor network. To do so, it is passed to the tunnel that encapsulates the packet into a USB frame and sends it to the mote sink that extracts the IPV6 packet from the USB frame and encapsulates it into a Zigbee frame. Once the Zigbee frame arrives to the destination mote, the TCP datagram is extracted from the IPV6 packet and passed to the TCP server of the mote that reads the message and executes it by turning on/off the appliance using I2C protocol.

\
As a second part of the two-way communication, the mote sends periodically sensor data to the middleware but again the communication is goes through several steps as depicted in figure 3.
\linebreak 
The mote reads periodically sends sensor data from the sensor, transforms the data and sends it. To send it the mote client connects to a TCP server hosted at the gateway. The IPV6 packet is encapsulated in a Zigbee frame that is forwarded to the mote  sink that extracts the IPV6 packet and  encapsulates it into a USB frame and forwarded to the gateway that reads the TCP datagram. Once the sensor data is at the gateway, the gateway forwards the sensor data to the middleware and if the link is down, the sensor data is temporarily stored in a database hosted in the gateway and once the link is up, all the stored data is sent to the middleware and cleared from the database.

\begin{figure}[htbp]
\centering
\includegraphics[height=110mm,width=90mm]{images/send_sensor_data_data_flow.jpg}
\caption{Data flow diagram for the mobile client sending on/off commands}
\label{fig:control_appliance}
\end{figure}

@@

\subsection{Network gateway packet transformation}
This is a very important component in the system. The issue is the following. The WSN network supports only IPV6 while other components such as the middleware and the mobile client do not necessary have an IPV6 address, but we still want all the components to communicate independently of the IP technology to be used. To do so, we have created a network packet transformation program. This program basically converts IPV4 to IPV6 and vice versa. To do so, it assigns virtual IPV4 addresses to IPV6 address holders and and IPV6 address to IPV4 address holders. With such a program, each player in the network has both an IPV4 and an IPV6 but is aware of only the one that is assigned to him. The other "virtual" address is known only at the level of the program installed at the gateway station between the WSN and the outside world. 
\\
 The flow of information works as follow; when a station wants to send requests to a mote, it will send IPV4 packet holding the request to the mote but by addressing it using its virtual IPV4 address. This packet will be sniffed by this packet transformation program that will extract the TCP datagram from the ip packet, create a new IPV6 packet specifying the source address as the virtual address of the host and the destination as the address of the mote and then append the TCP datagram to the newly created packet and send it to the mote sink packet forwarding component that is seen by the gateway as a network interface card. This leads to a complicated issue that is to be handled and which is that the program should keep track of the request responses in order to forward them correctly to the destination. 
\\
To solve such a problem, an algorithm has been created whose sole role is to mechanically compute the IPV6 address of the host based on its IPV4 and vice versa. This algorithm is based on function whose primary quality is the fact that it is bijective which means any IPV4 address is mapped to one and only one IPV6 function and vice versa. So whenever a request is coming, the source and destination address will be converted using this algorithm and this will make avoid the whole request response tracking part.
\section{Measurements}

@@

\bibliographystyle{plain}
\bibliography{myrefs}
